---
title: "The importance of amenities in AirBnb's for digital nomads in Barcelona"
output:
  pdf_document: default
  html_document:
    df_print: paged
date: "2023-03-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
# Load libraries
library(tidyverse)
library(dplyr)
library(tidyr)
library(ggplot2)

# Load data
counts <- read_csv("../../gen/analysis/input/counts.csv")
wide_df100 <- read_csv("../../gen/analysis/input/wide_df100.csv")
```

# Regression output

In the code below from `regression1.R` we illustrate once again how we obtain our regression output. This output is based on the dataframe `wide_df100` that contains information on all listings id's and the 100 most popular amenities.

```{r}
significant_amenities_100 <- c()
dep_vars <- names(wide_df100[3:102])

for (dep_var in dep_vars) {
  str <- paste(dep_var, "~ listing_type")  
  model <- lm(str, wide_df100)
  summary <- summary(model)
  
  if (summary$coefficients[2, 4] < 0.05) {
    
    if (summary$coefficients[2, 1] < 0) {
      significant_amenities_100 <- c(significant_amenities_100, dep_var)
    }
  }
}

```

The function and loop above returns amenities that are significantly more available in long-term listings compared to short-term listings. It stores this in the list called `significant_amenities_100`. If we print this list, we see the 20 amenities that are thus more available in long-term AirBnb's.

```{r echo=FALSE}
print(significant_amenities_100)
```

# Plots

We can visualize our results with the use of the `ggplot2` package. 
The plot below contains the 20 amenities that are more available in long-term listings. It shows the **proportion** of AirBnB's (both long-term and short-term listings) that contain these amenities. 

```{r echo=FALSE}
# Data input
ggplot(data = counts, aes(x = reorder(amenities, -prop_long), decreasing = TRUE)) +
  
# Barplot for short-term and long-term  
  geom_bar(aes(y = prop_long, fill = "Long-term"), position = "dodge2", stat = "identity") +
  geom_bar(aes(y = prop_short, fill = "Short-term"), position = "dodge2", stat = "identity") +
  
# Theme and text
  scale_fill_manual(values = c("lightcoral","brown4")) +
  labs(title = "Proportion of AirBnB listings containing amenities",
       x = "Amenities",
       y = "Proportion",
       fill = "") +
  theme_classic() + 
  theme(axis.text.x = element_text(angle = 50, hjust = 1)) + 
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2))

```






