---
title: "The importance of amenities in AirBnb's for digital nomads in Barcelona"
output:
  html_document:
    df_print: paged
date: "2023-03-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
# Load libraries
library(tidyverse)
library(dplyr)
library(tidyr)
library(ggplot2)

# Load data
counts <- read_csv("../../gen/analysis/input/counts.csv")
wide_df100 <- read_csv("../../gen/analysis/input/wide_df100.csv")

for (dep_var in dep_vars) {
  str <- paste(dep_var, "~ listing_type")  
  model <- lm(str, wide_df100)
  print(summary(model))
}
```

# Regression output

In the code below from `regression1.R` we illustrate once again how we obtain our regression output. This output is based in the dataframe `wide_df100` that contains information on all listings id's and the 100 most popular amenities.

```{r}
# Create a list with only significant amenities
significant_amenities_100 <- c()

for (dep_var in dep_vars) {
  str <- paste(dep_var, "~ listing_type")  
  model <- lm(str, wide_df100)
  summary <- summary(model)
  
  if (summary$coefficients[2, 4] < 0.05) {
    
    if (summary$coefficients[2, 1] < 0) {
      significant_amenities_100 <- c(significant_amenities_100, dep_var)
    }
  }
}

```

The function and loop above returns amenities that are significantly more available in long-term listings compared to short-term listings. It stores this in the list called `significant_amenities_100`. If we print this list, we see the 20 amenities that are thus more available in long-term AirBnb's.

```{r}
# Amenities significantly more available in long listings
print(significant_amenities_100)

```

# Plots

We can visualize our results with the use of the ggplot2 package:

```{r}
# Create dataset for plots
wide_df_significant <- wide_df100 %>% select(c(id, listing_type, significant_amenities_100))

```

```{r}
ggplot(data = wide_df_significant,
       mapping = aes(x = , fill = listing_type))

wide_df_significant %>%
  filter(listing_type == "long") %>%
  sum(wide_df_significant[3]) 

wide_df_sign_long <- wide_df_significant %>% filter(listing_type == "long") 


wide_df_sign_long[,c(1,3)]

ggplot(data = wide_df_significant , 
       mapping = aes(x = listing_type, fill = id))
```

```{r}
wide_df_significant %>% group_by(listing_type) %>% summarize(total = sum(c(has_Essentials)))

counts_100

```





